Figures for Paper

### 2021-03-23 paper_figures.Rmd
Update paper_figures.Rmd
Ignore the person who is not hom for both snps

```{r onlyshort}
boxplot_table %>% 
    filter(tissue_clean %in% 
               c("Frontal Cortex", 
                 "Lumbar Spinal Cord", 
                 "Cervical Spinal Cord",
                 "Motor Cortex", 
                 "Temporal Cortex",
                 "Cerebellum") )%>% 
    group_by(disease_group2,tissue_clean) %>% 
    mutate(n_sample = n_distinct(sample)) %>% 
    ungroup() %>% 
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>% 
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex")) %>% 
    ggplot(aes(x = detection_name, 
               y = inclusion_reads * 10^6,
               fill ="red")) + 
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1),outlier.colour = NA)) + 
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+ 
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) + 
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) + 
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom") 
```

@@

```{r}
detected_table_for_graph = clean_data_table %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>%
  filter(junction_reads_stmn2 >= 30) %>% 
  filter(junction_reads_unc13a >= 30) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,rs12608932,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_unc = log2((unc13a_cryptic_leaf_psi)/(stmn_2_cryptic_psi_leaf))) %>% 
  mutate(tissue_clean = gsub("_","\n",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  mutate(no_cong = ifelse(rs12608932 == "C/C" & rs12973192 == "C/G",8,3))

>>>>

```{r onlyshort}
boxplot_table %>% 
    filter(tissue_clean %in% 
               c("Frontal Cortex", 
                 "Lumbar Spinal Cord", 
                 "Cervical Spinal Cord",
                 "Motor Cortex", 
                 "Temporal Cortex",
                 "Cerebellum") )%>% 
    group_by(disease_group2,tissue_clean) %>% 
    mutate(n_sample = n_distinct(sample)) %>% 
    ungroup() %>% 
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>% 
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex")) %>% 
    ggplot(aes(x = detection_name, 
               y = inclusion_reads * 10^6,
               fill ="red")) + 
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1),outlier.colour = NA) + 
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+ 
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) + 
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) + 
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom") 
```

@@

```{r}
detected_table_for_graph = clean_data_table %>% 
  filter(!(rs12973192 == "C/G" & rs12608932 == "C/C")) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  filter(unc13a_cryptic_leaf_psi > 0 ) %>% 
  filter(stmn_2_cryptic_psi_leaf > 0 ) %>%
  filter(junction_reads_stmn2 >= 30) %>% 
  filter(junction_reads_unc13a >= 30) %>% 
  filter(grepl("Cortex",tissue_clean)) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,rs12608932,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(log2_unc = log2((unc13a_cryptic_leaf_psi)/(stmn_2_cryptic_psi_leaf))) %>% 
  mutate(tissue_clean = gsub("_","\n",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  mutate(no_cong = ifelse(rs12608932 == "C/C" & rs12973192 == "C/G",8,3)) %>% as.data.table()

#get out that person who is discongruous
